Implementing Real-Time Transport Services over an Ossified Network

### 2016-05-23 paper.tex
space

    It is instructive to compare the partially reliable send and receive
    functions to their TCP-like counterparts. The \texttt{send\_message()} call
    takes four additional parameters compared to the standard Berkeley Sockets
    API. These are 1) a message sequence number, that can be used to re-order
    messages and detect message loss; 2) a relative deadline, which is combined
    with an estimate of the current round-trip-time, and the time that the
    message has spent in the sending buffer, to determine if a message will
    arrive in time to be played-out; 3) the message sequence number of any
    message on which this depends, for example, of a video I-frame on which a
    P-frame is predicted; and 4) a sub-stream identifier, used, for example, to
    differentiate audio, video, sub-title, control, and repair streams.

>>>>

    It is instructive to compare the partially reliable send and receive
    functions to their Berkeley Sockets API counterparts. The
    \texttt{send\_message()} call takes four additional parameters. These are 1)
    a message sequence number, that can be used to re-order messages and detect
    message loss; 2) a relative deadline, which is combined with an estimate of
    the current round-trip-time, and the time that the message has spent in the
    sending buffer, to determine if a message will arrive in time to be
    played-out; 3) the message sequence number of any message on which this
    depends, for example, of a video I-frame on which a P-frame is predicted;
    and 4) a sub-stream identifier, used, for example, to differentiate audio,
    video, sub-title, control, and repair streams.
